### 2017-10-22 paper/sections/0_abstract.tex
paper: finish eval; touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Data center scale application developers are abandoning POSIX because the file
system metadata synchronization and serialization overheads of providing strong
consistency and durability are too costly -- and often unnecessary -- for their
applications.  Unfortunately, designing near-POSIX file systems excludes
applications that rely on strong consistency or durability, forcing developers
to re-write their applications or deploy them on a different system. Mounting
multiple systems in the global namespace forces users to (1) provision separate
storage clusters and (2) manually move data across systems.  We present a
framework and API that lets clients dynamically specify their
consistency/durability requirements and assign them to subtrees in the
namespace, allowing users to optimize subtrees within the same namespace for
different workloads.  We confirm the performance benefits of techniques
presented in related work but also explore new consistency/durability metadata
designs, all over the same storage system.  By custom fitting a subtree to a
create-heavy application, we show an 8\(\times\) speedup and scale further
(twice as many servers) than the system we implemented our prototype on.

>>>>

HPC and data center scale developers are abandoning POSIX IO because the file
system metadata synchronization and serialization overheads of providing strong
consistency and durability are too costly -- and often unnecessary -- for their
applications.  Unfortunately, designing file systems with weaker consistency or
durability excludes applications that rely on stronger guarantees, forcing
developers to re-write their applications or deploy them on a different system.
Mounting multiple systems in the global namespace forces users to (1) provision
separate storage clusters and (2) manually move data across systems.  We
present a framework and API that lets clients specify their
consistency/durability requirements and dynamically assign them to subtrees in
the same namespace, allowing users to optimize subtrees over time and space for
different workloads.  We confirm the performance benefits of techniques
presented in related work but also explore new consistency/durability metadata
designs, all integrated the same storage system.  By custom fitting a subtree
to a create-heavy application, we show 8\(\times\) speedup and 2\(\times\)
scale when compared to our baseline system.

### 2017-10-22 paper/sections/1_introduction.tex
paper: finish eval; touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users dynamically navigate
  the tradeoffs of different metadata protocols.

  \item This framework lets subtrees with different semantics co-exist in a
  global namespace. This is different than multiple mount points because
  there is no need to provision storage clusters for applications
  ({\it e.g.}, HDFS, CephFS) or move data between these systems.

  \item A prototype that lets developers custom fit subtrees to applications
  dynamically; this helps data center systems scale further than systems that
  use one strategy for the entire namespace.

@@

% Results
Our results confirm the assertions of ``clean-state" research systems that
decouple namespaces; specifically that the technique drastically improves
performance (104\(\times\) speed up) but we go a step further by quantifying
the costs of merging updates (7\(\times\) slow down) and maintaining durability
(\(10\times\) slow down). In our prototype, we get an 8\(\times\) speedup and
can scale to twice as many servers when we assign a more relaxed form of
consistency and durability to a subtree with a create heavy workload.
Meanwhile, other subtrees in the namespace maintain strong consistency and
durability with RPCs per operation.

We build on Ceph because it is used in cloud-based and data center
systems and has a presence in HPC~\cite{}.  More importantly,  we use Ceph as a
platform for exploring related work over the same storage system, which
facilitates an apples-to-apples comparison of the strategies themselves.

In the remainder of the paper, Section~\ref{sec:posix-overheads} quantifies the
cost of POSIX IO consistency and system-defined durability and
Section~\ref{sec:methodology-decoupled-namespaces} presents the Cudele
prototype and API. Section~\ref{sec:implementation} describes the Cudele
mechanisms and shows how re-using internal subsystems results in an
implementation of less than 500 lines of code. The evaluation in
Section~\ref{sec:evaluation} quantifies the overheads and performance gains of
explored and previously unexplored metadata designs.
Section~\ref{sec:related-work} places Cudele in the context of other related
work.

>>>>

  \item A framework and API for assigning consistency/durability policies 
  to subtrees in the file system namespace; this lets users navigate
  the tradeoffs of different metadata protocols.

  \item This framework lets subtrees with different semantics co-exist in a
  global namespace. We show how this scales further and performs better than
  systems that use one strategy for the entire namespace

  \item A prototype that lets users custom fit subtrees to applications
  dynamically.

@@

The last contribution lays the groundwork for future work on our prototype. It
improves the current practice of mounting different storage systems in a global
namespace because there is no need to provision dedicated storage clusters to
applications or move data between these systems.  For example, the results of a
Hadoop job do not need to be migrated into CephFS for other processing; instead
the user can change the semantics of the HDFS subtree into a CephFS subtree.
This may cause metadata/data movement to make things strongly consistent again
but this is superior to moving all data across file system boundaries. We
enable studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.

% Results
The results in this paper lay the groundwork for such a system and confirm the
assertions of ``clean-state" research that decouple namespaces; specifically
that the technique drastically improves performance (104\(\times\) speed up).
We go a step further by quantifying the costs of merging updates (7\(\times\)
slow down) and maintaining durability (\(10\times\) slow down). In our
prototype, we get an 8\(\times\) speedup and can scale to twice as many servers
when we assign a more relaxed form of consistency and durability to a subtree
with a create-heavy workload.  We build on Ceph because it is used in
cloud-based and data center systems and has a presence in HPC~\cite{}.  More
importantly,  we use Ceph as a platform for exploring related work over the
same storage system, which facilitates an apples-to-apples comparison of the
strategies themselves.

%In the remainder of the paper, Section~\ref{sec:posix-overheads} quantifies the
%cost of POSIX IO consistency and system-defined durability and
%Section~\ref{sec:methodology-decoupled-namespaces} presents the Cudele
%prototype and API. Section~\ref{sec:implementation} describes the Cudele
%mechanisms and shows how re-using internal subsystems results in an
%implementation of less than 500 lines of code. The evaluation in
%Section~\ref{sec:evaluation} quantifies the overheads and performance gains of
%explored and previously unexplored metadata designs.
%Section~\ref{sec:related-work} places Cudele in the context of other related
%work.

### 2017-10-22 paper/sections/3_posix_overheads.tex
paper: finish eval; touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% purpose of the journal
As shown in Figure~\ref{fig:journal}, in addition to the metadata journal,
CephFS also represents metadata in RADOS as a metadata store, where directories
and their file inodes are stored as objects.  The metadata server applies the
updates in the journal to the metadata store when the journal reaches a certain
size. The metadata store is optimized for recovery ({\it i.e.} reading) while
the metadata journal is write-optimized.

\begin{figure}[tb] \centering
\includegraphics[width=1\linewidth]{./figures/journal.png} 
\caption{CephFS has two views of the file system namespace: a journal of
metadata updates and a metadata store. For fault tolerance, they are stored in
the object store as segments and fragments, respectively.
\label{fig:journal}}
\end{figure}

>>>>

% purpose of the journal
In addition to the metadata journal, CephFS also represents metadata in RADOS
as a metadata store, where directories and their file inodes are stored as
objects.  The metadata server applies the updates in the journal to the
metadata store when the journal reaches a certain size. The metadata store is
optimized for recovery ({\it i.e.} reading) while the metadata journal is
write-optimized.

%\begin{figure}[tb] \centering
%\includegraphics[width=1\linewidth]{./figures/journal.png} 
%\caption{CephFS has two views of the file system namespace: a journal of
%metadata updates and a metadata store. For fault tolerance, they are stored in
%the object store as segments and fragments, respectively.
%\label{fig:journal}}
%\end{figure}

### 2017-10-22 paper/sections/5_implementation.tex
paper: finish eval; touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% how it works in CephFS
In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse.\\

% how i used it
\noindent\textbf{Cudele}: the ``RPCs" mechanism uses the metadata store to
service requests. Using code designed for recovery, ``Nonvolatile Apply" and
``Volatile Apply" replay updates onto the metadata store in memory and in the
object store, respectively.  When the clients are ready to merge their updates
back into the global namespace, they pass a binary file of  metadata updates to
the metadata server.

@@

The journal is the second way that CephFS represents the file system namespace;
it is a log of metadata updates that can materialize the namespace when the
updates are replayed onto the metadata store. The journal is a ``pile system";
writes are fast but reads are slow because state must be reconstructed.
Specifically, reads are slow because there is more state to read, it is
unorganized, and many of the updates may be redundant.\\

\noindent\textbf{Cudele}: the journal format is used by ``Stream", ``Append Client Journal",
``Local Persist", and ``Global Persist".  ``Stream" is the default
implementation for achieving global durability in CephFS but the rest of the
mechanisms are implemented by writing with the journal format.  By writing with
the same format, the metadata servers can read and use the recovery code to
materialize the updates from a client's decoupled namespace ({\it i.e.} merge).
These implementations required no changes to CephFS because the metadata
servers know how to read the events the library is writing.  By re-using the
journal subsystem to implement the namespace decoupling, Cudele leverages the
write/read optimized data structures, the formats for persisting events
(similar to TableFS's SSTables~\cite{ren:atc2013-tablefs}), and the functions
for replaying events onto the internal namespace data structures.

@@

The journal tool is used for disaster recovery and lets administrators view and
modify the journal. It can read the journal, export the journal as a file,
erase events, and apply updates to the metadata store.  To apply journal
updates to the metadata store, the journal tool reads the journal from object
store objects and replays the updates on the metadata store in the object
store.\\

\noindent\textbf{Cudele}: the external library the clients link into is based
on the journal tool. It already had functions for importing, exporting, and
modifying the updates in the journal so we re-purposed that code to implement
``Append Client Journal", ``Volatile Apply", and ``Nonvolatile Apply".

@@

In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For example, if a client or
metadata server is not caching the directory inode, all creates within that
directory will result in a lookup and a create request. If the directory inode
is cached then only the create needs to be sent.  The size of the inode cache
is configurable so as not to saturate the memory on the metadata server --
inodes in CephFS are about 1400
bytes\footnote{http://docs.ceph.com/docs/jewel/dev/mds\_internals/data-structures/}.
The inode cache has code for manipulating inode numbers, such as pre-allocating
inodes to clients.\\

\noindent\textbf{Cudele}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.\\

@@

In CephFS, inodes already store policies, like how the file is striped
across the object store or for managing subtrees for load balancing. These
policies adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other.  \\

\noindent\textbf{Cudele}: uses the large inodes to store consistency and
durability policies in the directory inode. This approach uses the File Type
interface from the Malacology programmable store
system~\cite{sevilla:eurosys17} and it tells clients how to access the
underlying metadata. The underlying implementation stores executable code in
the inode that calls the different Cudele mechanisms. Of course, there are many
security and access control aspects of this approach but that is beyond the
scope of this paper.

>>>>

% how it works in CephFS
In CephFS, the metadata store is a data structure that represents the file
system namespace. This data structure is stored in two places: in memory ({\it
i.e.} in the collective memory of the metadata server cluster) and as objects
in the object store. In the object store, directories and their inodes are
stored together in objects to improve the performance of scans.  The metadata
store data structure is structured as a tree of directory fragments making it
easier to read and traverse.

% how i used it
\textbf{Cudele}: the ``RPCs" mechanism uses the metadata store to
service requests. Using code designed for recovery, ``Nonvolatile Apply" and
``Volatile Apply" replay updates onto the metadata store in memory and in the
object store, respectively.  When the clients are ready to merge their updates
back into the global namespace, they pass a binary file of  metadata updates to
the metadata server.

@@

The journal is the second way that CephFS represents the file system namespace;
it is a log of metadata updates that can materialize the namespace when the
updates are replayed onto the metadata store. The journal is a ``pile system";
writes are fast but reads are slow because state must be reconstructed.
Specifically, reads are slow because there is more state to read, it is
unorganized, and many of the updates may be redundant.

\textbf{Cudele}: the journal format is used by ``Stream", ``Append Client Journal",
``Local Persist", and ``Global Persist".  ``Stream" is the default
implementation for achieving global durability in CephFS but the rest of the
mechanisms are implemented by writing with the journal format.  By writing with
the same format, the metadata servers can read and use the recovery code to
materialize the updates from a client's decoupled namespace ({\it i.e.} merge).
These implementations required no changes to CephFS because the metadata
servers know how to read the events the library is writing.  By re-using the
journal subsystem to implement the namespace decoupling, Cudele leverages the
write/read optimized data structures, the formats for persisting events
(similar to TableFS's SSTables~\cite{ren:atc2013-tablefs}), and the functions
for replaying events onto the internal namespace data structures.

@@

The journal tool is used for disaster recovery and lets administrators view and
modify the journal. It can read the journal, export the journal as a file,
erase events, and apply updates to the metadata store.  To apply journal
updates to the metadata store, the journal tool reads the journal from object
store objects and replays the updates on the metadata store in the object
store.

\textbf{Cudele}: the external library the clients link into is based
on the journal tool. It already had functions for importing, exporting, and
modifying the updates in the journal so we re-purposed that code to implement
``Append Client Journal", ``Volatile Apply", and ``Nonvolatile Apply".

@@

In CephFS, the inode cache reduces the number of RPCs between clients and
metadata servers. Without contention clients can resolve metadata reads locally
thus reducing the number of operations ({\it e.g.}, \texttt{lookup()}s).  For example, if a client or
metadata server is not caching the directory inode, all creates within that
directory will result in a lookup and a create request. If the directory inode
is cached then only the create needs to be sent.  The size of the inode cache
is configurable so as not to saturate the memory on the metadata server --
inodes in CephFS are about 1400
bytes\footnote{http://docs.ceph.com/docs/jewel/dev/mds\_internals/data-structures/}.
The inode cache has code for manipulating inode numbers, such as pre-allocating
inodes to clients.

\textbf{Cudele}: ``Nonvolatile Apply" uses the internal inode cache
code to allocate inodes to clients that decouple parts of the namespace and to
skip inodes used by the client at merge time.\\

@@

In CephFS, inodes already store policies, like how the file is striped
across the object store or for managing subtrees for load balancing. These
policies adhere to logical partitionings of metadata or data, like Ceph pools and file
system namespace subtrees. To implement this, the namespace data structure has
the ability to recursively apply policies to subtrees and to isolate subtrees
from each other.

\textbf{Cudele}: uses the large inodes to store consistency and
durability policies in the directory inode. This approach uses the File Type
interface from the Malacology programmable store
system~\cite{sevilla:eurosys17} and it tells clients how to access the
underlying metadata. The underlying implementation stores executable code in
the inode that calls the different Cudele mechanisms. Of course, there are many
security and access control aspects of this approach but that is beyond the
scope of this paper.

### 2017-10-22 paper/sections/6_results.tex
paper: finish eval; touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques
themselves\footnote{This is the reason we did not compare to other HPC or data
center systems; we are not claiming that our file system metadata protocols are
superior.}, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application.  We scope the evaluation to one metadata server and scale the
clients, which execute an extremely metadata intensive job in parallel. This
type of analysis shows the capacity and performance of a metadata server with
superior metadata protocols, which should be used to inform load balancing
across a metadata cluster. Load balancing with partitioning and replication can
be explored with something like Mantle~\cite{sevilla:sc15-mantle}.

@@

We run experiments on the same cluster and normalize results to control for
hardware differences and to make our results more generally applicable.  We use
a CloudLab cluster of 34 nodes, each with 16 2.4 GHz CPUs, 128GB RAM, and SSDs.
Each node uses Ubuntu 14.04 and has 1 monitor server, 3 object storage daemons,
1 metadata server, and 29 clients.  All daemons run as a single process which
is the default setting for Ceph. We develop on Ceph's Jewel release, version
10.2.1, which was released in May 2016.

This paper adheres to The Popper Convention~\cite{jimenez_popper_2016}, so
experiments presented here are available in the repository for this article.
Experiments can be examined in more detail, or even re-run, by visiting the
\texttt{[source]} link next to each figure. That link points to a Jupyter
notebook that shows the analysis and source code for that graph, which points
to an experiment and its artifacts.

@@

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5\text{KB}. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be
\(2.5\text{KB}*1\texttt{ million files} = 2.38\text{GB}\). Transfer times for
payloads of this size in most HPC/data cente networks are reasonable.

@@

% CITEME xiao:socc2015-shardfs CITEME HADOOP
Clients creating files in private directories is heavily studied in
HPC~\cite{weil:sc2004-dyn-metadata, ren:sc2014-indexfs, patil:fast2011-giga,
zheng:pdsw2014-batchfs, sevilla:sc15-mantle}, mostly due to
checkpoint-restart~\cite{bent_plfs_2009}.  But the workload also appears in
cloud workloads, where systems like Hadoop use the file abstraction to exchange
work units to workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event.

@@

The graph on the right of Figure~\ref{fig:composable-mechanisms} shows how
applications can compose mechanisms together to get the consistency/durability
guarantees they need.  We label the \(x\)-axis with systems that employ these
semantics, as described in Figure~\ref{fig:subtree-policies}.  Again, the
runtime of different semantics for subtrees in the same global namespace
normalized to the runtime of the ``Append Client Journal" mechanism (again,
just creating files in the client's in-memory journal).  We makes no guarantees
during execution of the mechanisms or when transitioning semantics -- the
semantics are guaranteed {\it once the mechanism completes}. So if servers fail
during a mechanism, metadata or data may be lost.

@@

{\it Durability \(<<\) Consistency:} The performance of these semantics
suggests that the overhead of consistency is much larger than the overhead of
durability. This conclusion should be stronger as we scale the number of files
because the cost of streaming the journal into the object store is constant.

% Weak Consistency benefit not due to metadata format
{\it Metadata Formats:} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats.

\textbf{Takeaway}: we confirm the performance benefits of other
well-established research systems but, more importantly, we show that the
Cudele mechanisms we propose are useful for building and evaluating different
consistency/durability semantics.

@@

\subsection{Use Case 2: Creates with Rogue Client}

Clients create files in private directories and a separate client, which we
call a ``rogue" client, creates files in each directory. This introduces false
sharing and the metadata server revokes capabilities on directories touched by
the rogue client. While HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.

% setup: 2cs sep dirs, 2cs DN, 1c malicious write
Next we show how Cudele can be programmed to block interfering clients. We use
the same problematic workload from Figure~\ref{fig:overhead-b}, where clients
write to their own private directories and another client interferes with a
stream of creates at 30 seconds.  We also have another client write to a
decoupled namespace and merge its updates at 90 seconds.  We equip each client
directory with the configuration: allocated\_inodes=100K,
interfere\_policy=block, consistency=RPCs, and durability=stream.

Each directory functions with ``RPCs"
and ``Stream" enabled -- which is the default implementation of CephFS. The only
difference is that we enable blocking on each subtree so while the tree behaves
like CephFS, all interfering operations will be returned with \texttt{-EBUSY}.
Note that IndexFS does a similar operation with leases except clients block.

% results
To show the benefits of this isolations, our results in
Figure~\ref{fig:allow-block} are plotted alongside the variance bars from
Figure~\ref{fig:overhead-b}. Because ``allow"/``interfere and
``block"/``isolated" have the same variability we draw the following three
conclusions: (1) clients that use the API to block interfering clients  get
the same performance as isolated clients, (2) there is a negligible effect on
performance for the extra work the metadata server does to return
\texttt{-EBUSY}, and (3) merging updates from the decoupled client has a
negligible effect on performance.

@@

% CITEME
Scientists use the file system to check the progress of jobs using
\texttt{ls}~\cite{CITEME}. The number of files or size of the files is
indicative of the progress. This practice is not too different from systems
that use the file system to manage the progress of jobs; Hadoop writes to
temporary files, renames them when complete, and creates a ``DONE" file to
indicate to the runtime that the task did not fail and should not be
re-scheduled on another node. In this scenario, Cudele users will not see the
progress of decoupled namespace since their updates are not globally visible.
To help scientists judge the progress of their jobs, Cudele clients have a
``namespace sync" that sends batches of updates back to the global namespace at
regular intervals.

@@

To show the contention at the metadata server of this approach, we scale the
number of journal merge events, each hitting different directories in the
namespace, in Figure~\ref{fig:mergescale}. The size of each journal is 100K
files, the maximum recommended directory size for CephFS. We also plot the cost
of RPCs with and without journaling; recall from Figure~\ref{fig:overhead}
that the scalability that max number of clients that the default metadata
server could support with RPCs is 18.

Merge requests are serialized at the metadata server; merging concurrently is
an optimization for future work. The current implementation has race conditions
because the metadata server recovery code was not designed to run in parallel
({\it i.e.} the metadata server never recovers with multiple threads). As a
result, the metadata server versions inodes and directory entries to ensure
that the recovered metadata is consistent.

Performance is better than RPCs because we place no restrictions on the
validity of metadata inserted into the journal and avoid touching poorly
scaling data structures. In other words, we can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files.
only appends \texttt{open()} requests to the journal. When the updates are
merged by the metadata server into the in-memory metadata store they never scan
growing data structures.  Had we implemented the ``Create" mechanism to include
\texttt{lookup()} commands before \texttt{open()} requests, we would have seen
the poor scaling that we see with the ``RPCs" mechanism.

\textbf{Takeaway}: the weakest form of consistency for creating files
({\it i.e.} not checking data structures for the validity of an update or
existence of a file) shows linear scalability and stable performance.

@@

%\subsection{Discussion}
%
%Cudele and the experiments we present here prompt many avenues for future work.
%The first is embeddable policies, where child subtrees have specialized
%features but still maintain the guarantees  of their parent subtrees. We
%already show how applciations can compose guarantees and control their
%performance, knobs that we did not have before, but embeddable policies are a
%way to compose the policies themsleves.  For example, a RAMDisk subtree is
%POSIX IO-compliant but relaxes durability constraints, so it can reside under a
%POSIX IO subtree that is strongly consistent. These embeddable policies should be
%controlled and enforced by Cudele.
%
%Second is the opportunity for adding hardware in strategic places to speed up
%the mechanisms that the application needs. In Figure~\ref{fig:mergescale} the
%performance of merging updates at the metadata server is limited by the speed
%of the disk. So applications that rely on merging many updates should consider
%equipping the metadata server with SSDs or more memory. This is a form of
%co-design that takes a ``dirty-slate" approach.
%
%Finally, performance prediction benefits from our cost quantification of each
%mechanism. Applications can use Cudele to microbenchmark their components and
%software, similar to what we did in Secion~\S\ref{sec:microbenchmarks}. Using
%those results, they can predict how much slower their system will be if they
%adopt stronger consistency or durability. This can also be a verification tool
%where performance that varies wildly from the predicted performance can be a
%red flag that something is wrong or that the bottleneck is not in the
%consistency or durability plane.

>>>>

Cudele lets users construct consistency/durability guarantees using
well-established research techniques from other systems; so instead of
evaluating the scalability and performance of the techniques themselves against
other file systems, we show that (1) the mechanisms we propose are useful for
constructing semantics used by real systems, (2) the techniques can work
side-by-side in the same namespace, and (3) the combination of these techniques
can help the system scale further when subtrees are coupled to the correct type
of application.  We scope the evaluation to one metadata server and scale the
number of parallel clients. This type of analysis shows the capacity and
performance of a metadata server with superior metadata protocols, which should
be used to inform load balancing across a metadata cluster. Load balancing
across a cluster of metadata servers with partitioning and replication can be
explored with something like Mantle~\cite{sevilla:sc15-mantle}.

@@

We run experiments on the same cluster and normalize results to control for
hardware differences and to make our results more generally applicable and
reproducible\footnote{ This paper adheres to The Popper
Convention~\cite{jimenez_popper_2016}, so experiments presented here are
available in the repository for this article.  Experiments can be examined in
more detail, or even re-run, by visiting the \texttt{[source]} link next to
each figure. That link points to a Jupyter notebook that shows the analysis and
source code for that graph, which points to an experiment and its artifacts.}.
We use a CloudLab cluster of 34 nodes, each with 16 2.4 GHz CPUs, 128GB RAM,
and SSDs.  Each node uses Ubuntu 14.04 and We develop on Ceph's Jewel release,
version 10.2.1, which was released in May 2016. All daemons run as a single
process (the default setting for Ceph) and the Ceph
components\footnote{http://docs.ceph.com/docs/jewel/rados/} are: 1 monitor, 3
object storage daemons, 1 metadata server, and 29 clients.

@@

{\it Journal Size:} We measure the amount of storage per journal update to be
about 2.5\text{KB}. The storage footprint scales linearly with the number of
metadata creates and suggests that updates for a million files would be 2.5KB
\(*\) 1 million files \(=\) 2.38GB. Transfer times for payloads of this size in
most HPC/data cente networks are reasonable.

@@

% CITEME xiao:socc2015-shardfs CITEME HADOOP
Clients creating files in private directories is heavily studied in
HPC~\cite{weil:sc2004-dyn-metadata, ren:sc2014-indexfs, patil:fast2011-giga,
zheng:pdsw2014-batchfs, sevilla:sc15-mantle}, mostly due to
checkpoint-restart~\cite{bent_plfs_2009}.  But the workload also appears in
cloud workloads, where systems like Hadoop use the file abstraction to exchange
work units to workers or to indicate when jobs
complete~\cite{shvachko:login2012-hdfs-scalability}. A more familiar example is
uncompressing an archive ({\it e.g.}, \texttt{tar xzf}), where the file system
services a flash crowd of creates across all directories as shown in
Figure~\ref{fig:overhead-creates}.  We use this as a microbenchmark because it
allows us to control the size of the log, since each create creates a single
journal event. The workload is clients creating 100K files in private
directories in the same global namespace.

@@

The graph on the right of Figure~\ref{fig:composable-mechanisms} shows how
applications can compose mechanisms together to get the consistency/durability
guarantees they need in a global namespace.  We label the \(x\)-axis with
systems that employ these semantics, as described in
Figure~\ref{fig:subtree-policies}.  Again, the runtime is normalized to
creating files in the client's in-memory journal.  We make no guarantees
during execution of the mechanisms or when transitioning semantics -- the
semantics are guaranteed {\it once the mechanism completes}. So if servers fail
during a mechanism, metadata or data may be lost.

\textbf{Takeaway}: we confirm the performance benefits of other
well-established research systems but, more importantly, we show that the
Cudele mechanisms we propose are useful for building and evaluating different
consistency/durability semantics.\\

To show the contention at the metadata server, in Figure~\ref{fig:mergescale}
we scale the umber of clients for the RPC per operation strategy used by many
POSIX IO systems and the decoupled namespace strategy used by DeltaFS. For
RPCs, we scale the number of clients making requests to the metadata server and
for the decoupled bars, we scale the number of concurrent journal merge
requests. So for the 30 clients data point, we are measuring the operations per
second for 30 client journals that land on the metadata server at the same
time. The ``create \& merge" bar adds the time it takes for clients to generate
the journal of events in parallel.

%Merge requests are serialized at the metadata server; merging concurrently is
%an optimization for future work. The current implementation has race conditions
%because the metadata server recovery code was not designed to run in parallel
%({\it i.e.} the metadata server never recovers with multiple threads). As a
%result, the metadata server versions inodes and directory entries to ensure
%that the recovered metadata is consistent.

This workload scales further with decoupled namespaces because the metadata
server is not overwhelmed with RPC requests. Compared to
Figure~\ref{fig:overhead-c} we can scale to 40 clients which is more than
double the capacity of a single metadata server using the RPC strategy to
maintain strong consistency. Related work has pointed to on-disk metadata
format as the primary factor for improved scalability; but our results show
that the weakened consistency and durability enables the scalability
improvements. The on-disk metadata formats in this experiment are the same for
all schemes.

The performance of decoupled namespaces is better than RPCs because we place no
restrictions on the validity of metadata inserted into the journal and avoid
touching poorly scaling data structures. We can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files
({\it i.e.} only append \texttt{open()} requests to the journal).  When the
updates are merged by the metadata server into the in-memory metadata store
they never scan growing data structures.  Had we implemented the ``Create"
mechanism to include \texttt{lookup()} commands before \texttt{open()}
requests, we would have seen the poor scaling that we see with the ``RPCs"
mechanism.

@@

%{\it Durability \(<<\) Consistency:} The performance of these semantics
%suggests that the overhead of consistency is much larger than the overhead of
%durability. This conclusion should be stronger as we scale the number of files
%because the cost of streaming the journal into the object store is constant.
%
% Weak Consistency benefit not due to metadata format

\textbf{Takeaway}: the ability to couple well-established techniques to
specific applications allows the global namespace to scale further and perform
better.

@@

\subsection{Use Case 2: Creates with Interferring Client}

Next we show how Cudele can be programmed to block interfering clients using
the same problematic workload from Figure~\ref{fig:overhead-b}. In this
workload, clients create files in private directories and a separate client
creates files in each directory. This introduces false sharing and the metadata
server revokes capabilities on directories touched by the interfering client. While
HPC tries to avoid these situations with
workflows~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs}, it still
happens in distributed file systems when users unintentionally access
directories in a shared file system.  We also have another client write to a
decoupled namespace and merge its updates at 90 seconds.  We only scale to 15
clients because the performance variability of a nearly overloaded metadata
server, in our case 18 clients, is too high.

Figure~\ref{fig:block-allow} plots the overhead of the slowest client and the
error bars are the standard deviation of 3 runs.  ``Interfere (Fig 3c)" is the
result from Figure~\ref{fig:overhead-b}; ``Interfere" uses the allow/block API
to return \texttt{-EBUSY} to interferring clients; and ``Isolated" is the
baseline performance without an interferring Each subtree has ``RPCs" and
``Stream" enabled.  Results results are normalized to the runtime of a single
client creating files in a directory. Note that IndexFS has a similar behavior
to ``interfere" with leases, except clients block.

We draw three conclusions: (1) clients that use the API to block interfering
clients  get the same performance as isolated clients, (2) there is a
negligible effect on performance for the extra work the metadata server does to
return \texttt{-EBUSY}, and (3) merging updates from the decoupled client has a
negligible effect on performance.

@@

% CITEME
Scientists use the file system to check the progress of jobs using
\texttt{ls}~\cite{CITEME}. The number of files or size of the files is
indicative of the progress. This practice is not too different from systems
that use the file system to manage the progress of jobs; Hadoop writes to
temporary files, renames them when complete, and creates a ``DONE" file to
indicate to the runtime that the task did not fail and should not be
re-scheduled on another node. In this scenario, Cudele users will not see the
progress of decoupled namespaces since their updates are not globally visible.
To help scientists judge the progress of their jobs, Cudele clients have a
``namespace sync" that sends batches of updates back to the global namespace at
regular intervals.

@@

\textbf{Takeaway}: syncing namespace updates has up to a 9\% overhead and can
be tuned depending on the users preference but, more importantly, the API gives
users fine-grain control of their consistency/durability to support current
practices or experimental workflows.

@@

\subsection{Discussion and Future Work}

Cudele and the experiments we present here prompt many avenues for future work.
First is quantifying the benefits of dynamically changing the semantics of a
subtree from stronger to weaker guarantees (or vice versa), as described in the
introduction. Second is embeddable policies, where child subtrees have
specialized features but still maintain the guarantees  of their parent
subtrees. We already show how applciations can compose guarantees and control
their performance, knobs that we did not have before, but embeddable policies
are a way to compose the policies themsleves.  For example, a RAMDisk subtree
is POSIX IO-compliant but relaxes durability constraints, so it can reside
under a POSIX IO subtree that is strongly consistent. These embeddable policies
should be controlled and enforced by Cudele.  Finally, performance prediction
benefits from our cost quantification of each mechanism. Applications can use
Cudele to microbenchmark their components and software, similar to what we did
in Secion~\S\ref{sec:microbenchmarks}. Using those results, they can predict
how much slower their system will be if they adopt stronger consistency or
durability.  This is a form of co-design that takes a ``dirty-slate" approach
but building just the guarantees the application needs from existing
implementations.  This can also be a verification tool where performance that
varies wildly from the predicted performance can be a red flag that something
is wrong or that the bottleneck is not in the consistency or durability plane.

%Second is the opportunity for adding hardware in strategic places to speed up
%the mechanisms that the application needs. In Figure~\ref{fig:mergescale} the
%performance of merging updates at the metadata server is limited by the speed
%of the disk. So applications that rely on merging many updates should consider
%equipping the metadata server with SSDs or more memory. 
%

### 2017-10-22 paper/sections/7_conclusion.tex
paper: finish eval; touch up intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Relaxing consistency and durability semantics in the file system is a
double-edged sword. While it achieves better performance and scalability, it
alienates applications that rely on strong consistency and durability. Cudele
lets users assign consistency and durability guarantees to subtrees in
the global namespace, giving users a wide range of policies and
optimizations that can be custom fit to the application. Using Cudele, we
compare related work on the same file system and conclude that strong
consistency can cause a 104\(\times\) slow down while merging updates and
maintaining durability only have between a \(7-10\times\) slow down.

>>>>

Relaxing consistency and durability semantics in the file system is a
double-edged sword. While it achieves better performance and scalability, it
alienates applications that rely on strong consistency and durability. Mounting
other systems to the global namespace is convenient but wastes resources and
incurs data movement.  Cudele lets users assign consistency and durability
guarantees to subtrees in the global namespace, which can be custom fit to the
application. Using Cudele, we show how applications can co-exist and perform
well in a global namespace and lay the groundwork for new systems that
dynamically change consistency/durability guarantees to avoid provisioning
dedicated storage clusters and moving large amounts of data.
